\input{Current Report/format}
\usepackage{hyperref}
\usepackage{array}
\usepackage{makecell}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\begin{document}
\fontsize{12}{13}
\selectfont

\begin{center}
\textbf{\Large{\bf Safe Deployment of Small Unmanned Aerial Systems\\}}
\vspace{6pt}
\textbf{\Large{\bf through On-Board Monitoring and Assessment}}\\ 
\vspace{6pt}
\textbf{NRA ROA –2019 NNH19ZEA001N-SWS\\
B.5 System-Wide Safety (SWS) Project}\\ \vspace{6pt}
\underline{\smash{\emph{Monthly Report: October 2021}}} \\ \vspace{6pt}
PI: Jane Cleland-Huang, (JaneHuang@nd.edu)\\
co-I: Myra Cohen, (mcohen@iastate.edu)\\
co-I: Nitesh Chawla,(nchawla@nd.edu)\\
\end{center}

\section{General Overview}
Our work this month has focused on exploring techniques for analysing and interpreting flight logs and on understanding the configurable features that are particularly impactful for causing runtime configuration problems.  In the following task decomposition, we have highlighted the tasks that we have worked on this month (blue), completed tasks (yellow), and currently inactive -- but not yet completed tasks (gray). 

\input{Task1}
\input{Task2}
\input{Task3}



\section{Other Goals}
\noindent Work on the following research goals is either not yet started or in very preliminary stages:
\subsection{Safety Analysis and Assurance: }
Our  goal  is  not  only  to  detect  anomalies,  but  also  to  diagnose  them,  gain  understanding of  their  underlying  causes,  and  ultimately  to  identify  mitigations.   We  plan to  adopt  a systematic  safety-analysis  and  assurance  approach  using  Fault  Tree  Analysis  (FTA)  and Safety-Assurance Cases (SAC). {\bf No progress was been made on this goal in August.}
\subsection{ Architectural Analysis and Integration: }
A key component of this research involves evaluating existing NAS and SWIM architecturesto determine how well they can support in-time assessment functions – such as our Dronolytics  solution.  We  will  design,  implement,  and  deploy  a  highly  modular,  scalable, low-power consumption prototype system with capabilities to interface with existing NAS infrastructures. 


\section{Questions to NASA and other updates: }
We will discuss what kind of paper we can submit to the SWS event at https://www.aiaa.org/aviation. One possibility is a summary of early results across our current solution with a proof-of-concept integration into our onboard autopilot software. 
Our goals are (1) summarize some of the work we are doing, (2) don't replicate papers we are submitting to ICCPS and ISPN, and (3) possibly make our first foray into a proposed architecture with proof-of-concept integration to our own current onboard UAV architectural solutions.  
Lilly please let us know if you'd like to participate in this paper as a co-author.
\end{document}



