\section{Data Collection and Annotation Infrastructure}
Task T1 focuses on establishing infrastructure for the project. Two Notre Dame students continue to build the website and backend.

\sethlcolor{col}

\begin{itemize}[leftmargin=0em]

\item[] 

\begin{itemize}[leftmargin=*]
\item {\bf Task 1.1:}
Develop data collection and annotation infrastructure.\vspace{-10pt}
\begin{table}[h!]
\addtolength{\tabcolsep}{-6pt}
%\small
\hspace*{.38cm}\begin{tabular}{L{11.1cm}L{1.5cm} L{2cm} L{1.4cm} }
{\bf \scriptsize \sc Subtask}&{\bf \scriptsize \sc Started}&{\bf \scriptsize \sc Target}&{\bf \scriptsize \sc Status}\\ \hline

\large a.\hl{~Develop \& deploy website for collecting flight logs}.&06/21&11/21&Active\\
\sethlcolor{col2}
\large b.\hl{~Develop tools for visualizing \& analyzing flight anomalies}.&06/21&11/21&Active\\
\sethlcolor{col2}
\large c.\hl{~Build collections of anomalous flight logs}&07/21&Continual&Active\\
\large d.~Construct labeled dataset of flight log anomalies. &&&Planned\\
\end{tabular}
\end{table}\vspace{-8pt}

\item{\bf Task 1.2:} Create infrastructure for working with simulated data. \vspace{-10pt}
\normalsize
\begin{table}[h!]
\addtolength{\tabcolsep}{-5.6pt}
\normalsize
\hspace*{.38cm}\begin{tabular}{L{11.1cm}L{1.5cm} L{2cm} L{1.4cm} }
{\bf \scriptsize \sc Subtask}&{\bf \scriptsize \sc Started}&{\bf \scriptsize \sc Target}&{\bf \scriptsize \sc Status}\\ \hline
\sethlcolor{col}
\large a.~\hl{Establish environment for collecting simulated flight logs}&06/21&09/21&Active\\
\large b.~Collect paired flight logs for simulated \& physical flights.&&&Planned\\
\large c.~Establish test oracle \& statistically compare flight data.&&&Planned\\
\large d.~Create cloud service for runtime off-board data analysis &&&Planned\\
\end{tabular}
\end{table}
\end{itemize}
\end{itemize}
\vspace{-12pt}

Specific activities related to data collection infrastructure that we have performed during this period have focused on the following:
\begin{itemize}[leftmargin=*]
    \item {\bf Backend Server for Data Collection} {\it  [Task T1.1a]: } Our team has implemented a basic backend SQL server integrated with Django. It is undergoing tests.
    \item {\bf Front-end Data Collection website: } The previous front-end work was a summer project with two UG students. We do not plan further activities until the backend server (at least an initial version) is deployed.
    \item {\bf Initial Data Collation} {\it  [Task 1.1b]: }
    There were no further collection activities this month as we are currently using the Ardupilot and px4 dataset that we have already downloaded (px4) and collected (ardupilot).
\item{\bf Onboard Infrastructure} {\it [Task 1.2a]: }We have completed and deployed a set of software-hardware tests for ensuring that our planned flight controller is compatible with our autopilot system.  The overall system architecture will provide the infrastructure we need to support the architectural aspects of this project.  \end{itemize}

\subsection*{Summarized Metrics}
No change in collected data expected until after the website is deployed.

\begin{table}[h!]
    \centering 
    \begin{tabular}{|l|l|c|c|c|} \hline
        &{\bf Metric} & {\bf PX4} & {\bf Ardupilot} & {\bf Other}  \\ \hline
        1.& Total No. of Physical Logs collected&77357&700&0\\ \hline
        2.& Total No. of Physical Logs collected with anomalies&tbd&$>$30&0\\ \hline 
        3.& Total No. of Physical Logs collected with annotated anomalies&0 &0&0\\ \hline  
        4.& Total No. of Simulated Logs collected&0&0&0\\ \hline
        5.& Total No. of Simulated Logs collected with anomalies&0 &0&0\\ \hline 
        6.& Total No. of Simulated Logs collected with anomalies labeled&0 &0&0\\ \hline  
    \end{tabular}
    \newline Note: Still analyzing all the data we imported as it lacks some meta-data.
\end{table}

\subsection*{Next Steps: }
We will continue development and deployment of the website, including infrastructure of the backend database, the onboard collection mechanisms, and the large-scale simulation.