\section{Data Collection and Annotation Infrastructure}
Task T1 focuses on establishing infrastructure for the project. 
Our goal is to have much of the basic infrastructure developed by the end of November. the infrastructure for uploading files and annotating them fully deployed by the end of November (Task 1.1a). To that end we have engaged in the following infrastucture building tasks:

\sethlcolor{col}

\begin{itemize}[leftmargin=0em]

\item[] 

\begin{itemize}[leftmargin=*]
\item {\bf Task 1.1:}
Develop data collection and annotation infrastructure.\vspace{-10pt}
\begin{table}[h!]
\addtolength{\tabcolsep}{-6pt}
%\small
\hspace*{.38cm}\begin{tabular}{L{11.1cm}L{1.5cm} L{2cm} L{1.4cm} }
{\bf \scriptsize \sc Subtask}&{\bf \scriptsize \sc Started}&{\bf \scriptsize \sc Target}&{\bf \scriptsize \sc Status}\\ \hline

\large a.\hl{~Develop \& deploy website for collecting flight logs}.&06/21&11/21&Active\\
\sethlcolor{col2}
\large b.\hl{~Develop tools for visualizing \& analyzing flight anomalies}.&06/21&11/21&Active\\
\sethlcolor{col2}
\large c.\hl{~Build collections of anomalous flight logs}&07/21&Continual&Active\\
\large d.~Construct labeled dataset of flight log anomalies. &&&Planned\\
\end{tabular}
\end{table}\vspace{-8pt}

\item{\bf Task 1.2:} Create infrastructure for working with simulated data. \vspace{-10pt}
\normalsize
\begin{table}[h!]
\addtolength{\tabcolsep}{-5.6pt}
\normalsize
\hspace*{.38cm}\begin{tabular}{L{11.1cm}L{1.5cm} L{2cm} L{1.4cm} }
{\bf \scriptsize \sc Subtask}&{\bf \scriptsize \sc Started}&{\bf \scriptsize \sc Target}&{\bf \scriptsize \sc Status}\\ \hline
\sethlcolor{col}
\large a.~\hl{Establish environment for collecting simulated flight logs}&06/21&09/21&Active\\
\large b.~Collect paired flight logs for simulated \& physical flights.&&&Planned\\
\large c.~Establish test oracle \& statistically compare flight data.&&&Planned\\
\large d.~Create cloud service for runtime off-board data analysis &&&Planned\\
\end{tabular}
\end{table}
\end{itemize}
\end{itemize}
\vspace{-12pt}

Specific activities related to data collection infrastructure that we have performed during this period have focused on the following:
\begin{itemize}[leftmargin=*]
    \item {\bf Backend Server for Data Collection} {\it  [Task T1.1a]: } We have had several discussions with our Computing Research Center (CRC) who were originally going to deploy the backend database for us.  Due to some internal CRC circumstances they are no longer able to do this.  Instead we will develop the full website ourselves and host on a cloud-based service.  We have just recruited a Senior UG student (Raj Mehta) who will deploy an initial Django website and then connect the front end UI. While we experienced a delay on this task, we still anticipate meeting our scheduled deployment.
    \item {\bf Front-end Data Collection website: } The previous front-end work was a summer project with two UG students. We do not plan further activities until the backend server (at least an initial version) is deployed.
    \item {\bf Initial Data Collation} {\it  [Task 1.1b]: }
    There were no further collection activities this month as we are currently using the Ardupilot and px4 dataset that we have already downloaded (px4) and collected (ardupilot).
\item{\bf Onboard Infrastructure} {\it [Task 1.2a]: }
We have continued work on developing the onboard infrastructure and a large-scale, robust, realistic simulation environment for ecosystem experimentation.  Once released, each simulation will support up to 230 simultaneous UAVs (each with a full physics engine simulation and onboard camera) across any region. We will report on this further once it is fully deployed and operational (hopefully next month). While we have previously deployed simulations with 200+ drones, the new simulation environment is needed as it introduces greater fidelity, interactivity between the drones, and an integrated environment for supporting both onboard flight log analysis as well as off-board data aggregation and analysis. We have addressed several challenging technical problem but we are making steady progress.  Once deployed, this will speed up our work significantly and enable experiments at scales and degrees of fidelity not feasible with physical drones alone.  \end{itemize}

\subsection*{Summarized Metrics}
As building a large, annotated dataset is a key goal of the project, we track progress towards this goal. We did not extend this part of the dataset since the last report; however, Cohen's team are working on a subset of same dataset (px4) and ultimately we will merge results into a single dataset.

\begin{table}[h!]
    \centering 
    \begin{tabular}{|l|l|c|c|c|} \hline
        &{\bf Metric} & {\bf PX4} & {\bf Ardupilot} & {\bf Other}  \\ \hline
        1.& Total No. of Physical Logs collected&77357&700&0\\ \hline
        2.& Total No. of Physical Logs collected with anomalies&tbd&$>$30&0\\ \hline 
        3.& Total No. of Physical Logs collected with annotated anomalies&0 &0&0\\ \hline  
        4.& Total No. of Simulated Logs collected&0&0&0\\ \hline
        5.& Total No. of Simulated Logs collected with anomalies&0 &0&0\\ \hline 
        6.& Total No. of Simulated Logs collected with anomalies labeled&0 &0&0\\ \hline  
    \end{tabular}
    \newline Note: Still analyzing all the data we imported as it lacks some meta-data.
\end{table}

\subsection*{Next Steps: }
The majority of effort next month will go to infrastructure of the backend database, the onboard collection mechanisms, and the large-scale simulation.