\input{Current Report/format}
\usepackage{hyperref}
\usepackage{array}
\usepackage{makecell}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\begin{document}
\fontsize{12}{13}
\selectfont

\begin{center}
\textbf{\Large{\bf Safe Deployment of Small Unmanned Aerial Systems\\}}
\vspace{6pt}
\textbf{\Large{\bf through On-Board Monitoring and Assessment}}\\ 
\vspace{6pt}
\textbf{NRA ROA –2019 NNH19ZEA001N-SWS\\
B.5 System-Wide Safety (SWS) Project}\\ \vspace{6pt}
\underline{\smash{\emph{Monthly Report: November 2021}}} \\ \vspace{6pt}
PI: Jane Cleland-Huang, (JaneHuang@nd.edu)\\
co-I: Myra Cohen, (mcohen@iastate.edu)\\
co-I: Nitesh Chawla,(nchawla@nd.edu)\\
\end{center}

\section{General Overview}
A major emphasis of the Notre Dame Team's work this month was on completing and submitting a paper to the International Conference on Information Processing in Sensor Networks (IPSN). Please see attached paper.

\noindent {\bf Md.Nafee Al Islam, Yihong Ma, Nitesh Chawla, Jane Cleland-Huang, `Detecting and Diagnosing Anomalies in the Sensor Data of small Unmanned Aerial Systems'.} Under Review.

\noindent This was an ND team effort as the work started early in the summer before the Iowa State (ISU) team students came online. 

\noindent The entire team (ND and ISU) contributed to the abstract submitted to the  2022 AIAA Aviation Forum entitled:
{\bf Towards Real-Time Safety Analysis of Small Unmanned Aerial Systems in the National Airspace}, Category: Air Transportation Systems: Integration and Operation of AAM/UAM/UAS in the NAS.

This progress report summarizes some of the work from the IPSN paper, provides a more detailed account of ISU activities, and summarizes joint tasks. In the following task decomposition, we have highlighted the tasks that we have worked on this month (blue), completed tasks (yellow), and currently inactive -- but not yet completed tasks (gray). 

\input{Task1}
\input{Task2}
\input{Task3}



\section{Other Goals}
\noindent Work on the following research goals is either not yet started or in very preliminary stages:
\subsection{Safety Analysis and Assurance: }
Our  goal  is  not  only  to  detect  anomalies,  but  also  to  diagnose  them,  gain  understanding of  their  underlying  causes,  and  ultimately  to  identify  mitigations.   We  plan to  adopt  a systematic  safety-analysis  and  assurance  approach  using  Fault  Tree  Analysis  (FTA)  and Safety-Assurance Cases (SAC). {\bf No progress was been made on this goal in August.}
\subsection{ Architectural Analysis and Integration: }
A key component of this research involves evaluating existing NAS and SWIM architecturesto determine how well they can support in-time assessment functions – such as our Dronolytics  solution.  We  will  design,  implement,  and  deploy  a  highly  modular,  scalable, low-power consumption prototype system with capabilities to interface with existing NAS infrastructures. 


\section{Questions to NASA and other updates: }
Please could you give us more details about the 6-month review? Primarily our understanding is that we will present the current status of our work and plans for the next 6 months.  It would be great if we could set a time/date for the review.  

Thanks for the extension on the report this month. It was really helpful as we have had a busy submission cycle over the past two weeks including the IPSN paper and the Aviation abstract (both attached).

\end{document}



